---
title: "Eating Out"
author: "Leonel D. Bautista"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, warning=FALSE}
#GSS <-read_dta(file="GSS1996.dta")
GSS <- readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Graphical Results   

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")
```

There exists a noticeable contrast in the dining-out habits between the white population and other racial groups, as indicated by the percentage-based graphical data. Nevertheless, when examining the non-percentage data, it becomes evident that the sample size for non-white racial groups is considerably smaller compared to that of the white population.   

# Numerical Results   

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```   

The numerical data findings validate the observations made in the graphical data, indicating a substantial percentage (less than 10%) difference in dining out habits between individuals of black ethnicity and those of white/other races. Nevertheless, the considerable proportion of the overall population that falls into the categories of either eating out or refraining from it, among whites, underscores the significantly larger sample size of the white racial group compared to the other two racial categories.   

# Inferential Results   

```{r}
chisqtestGC(table1)
```   

The outcome of the chi-squared test indicates that we possess a chi-squared statistic significantly exceeding the 2 degrees of freedom provided by the data. Moreover, a critical p-value is indeed present in the data. There exists a distinction within the dataset.   

```{r}
fisherXY(mydata$race,mydata$eatout,printAll=TRUE,confL = 0.99)
```   

We observe that the critical p-value was situated in the context of the relationship between the black and white races. We displayed all the p-values associated with the various combinations, and this reveals that the sole distinction is found within the "black" and "white" factors.   

# Discussion and Conclusion

Based on the culmination of the data, it is evident that there exists a discernible distinction within the data set. Consequently, we are inclined to reject the null hypothesis ($H_0$), signifying a statistically significant variance in the data. Both the visual representations and numerical analyses concur in demonstrating that the "white" factor exhibits a higher frequency of occurrence compared to other factors. When considering a 99% confidence interval, the critical p-value only detects a disparity in the relationship between the "black" and "white" factors. The likelihood of this occurrence being purely coincidental stands at 2.2 to 1 odds. Furthermore, the data sets size is substantial enough to reasonably exclude the possibility that these findings are a result of sampling error or a small sample size.   



